Fusion Moves for Correlation Clustering

### 2014-11-12 paper/egpaper_for_review.tex
removed some links and improved proposal generation

%------------------------------------------------------------------------
\section{Correlation-Clustering-Fusion}\label{sec:cc_fm}

Fusion move algorithms~\cite{Lempitsky-2010} are a popular technique 
for large scale discrete energy minimization problems.
They iteratively fuse two node labelings by optimizing over the label space spanned by those.
Different fusion algorithms vary in the proposals and method used for the auxiliary fusion problem~\cite{kappes_2014_ws}.

As fusion algorithms work with node labelings, % \cf Eq.~\ref{eq:nodeproblem},
we face the problem that the node coloring is ambiguous and has no semantic meaning.
This causes that a fusion move is not well defined, because different choices of colors 
lead to different auxiliary problems, as shown in Fig.~\ref{fig:fusion_abiguty}.

In the following, we propose a more suitable fusion move for correlation
clustering which works on the edge domain.
%
Given two proposal solutions $y'$ and $y''$,
$\mathcal{E}^0_{\breve{y}}$ is the set of edges
which are uncut in $y'$ and $y''$.
%
\begin{align}
\breve{y}_{ij}    & = \max\{ y_{ij}', y_{ij}''\}  & \forall {ij}\in E\\  % y' \cup y'' \\
\mathcal{E}^0_{\breve{y}}  & =  \{ (i, j) \; | \; \breve{y}_{ij} = 0 \}
\end{align}
%
The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
with additional \emph{must-link constraints} for all edges in $\mathcal{E}^0_{\breve{y}}$.
%
\begin{align}
  y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
      &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in \mathcal{E}^0_{\breve{y}} \nonumber
\end{align}
%
By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy,
because $y'$ and $y''$ are feasible solutions for problem~\ref{eq:fusion_move_a}.
%\begin{align}
%  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
%\end{align}
%

@@

\noindent \textbf{Randomized HierarchicalClustering (RHC):}
%\subsubsection{Randomized HierarchicalClustering (RHC)}
%
To generate fast energy aware proposals we can use energy
based hierarchical clustering (EHC) as defined in sec.~\ref{sec:ehc}.
EHC follows the energy function, therefore the \emph{quality}
of the proposals is high.
To get \emph{diversity} among the different proposal,
we add normal distributed noise with a standard deviation of $\sigma_{ehc}$
to each edge weight.
To get proposals of the desired \emph{size}, we can use a
different stop condition in EHC, and stop when a certain number of connected
components is reached.

@@

\noindent \textbf{Randomized Watersheds (RWS):}
%\subsubsection{Randomized Watersheds (RWS)}
%
The edge weighted watershed algorithm \cite{meyer_2013}
with random seeds can be used to get
cheap proposals.
To improve \emph{quality} we do not use $n$ seeds distributed uniformly
over all nodes but use the following.
Draw $n/k$ random edges only the negative edges,
and give the two nodes of each ``seed-edge'' a different seed.
Doing so, a random subset of negative edges is forced
to be cut within each proposal.
For additional \emph{diversity} randomness, noise can be added to
the edge weighs.

@@

For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}
of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{https://github.com/opengm/opengm}}.
For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we try the public available implementation in OpenGM\footref{opengm-master}
of Kappes~\etal. We realize that their implementation has some limitations on large problems and make the following modifications.
Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
This procedure is one magnitude faster, but might cause a few extra outer iterations.
In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
We use the public available code of Micha Elsner\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
While this implementation uses full adjacency matrixes it does not scale as well as the algorithm can and therefor can not be applied on all datasets.
We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.

>>>>

%------------------------------------------------------------------------
\section{Correlation-Clustering-Fusion Moves}\label{sec:cc_fm}

Fusion moves as defined in \cite{Lempitsky-2010} work
in the node domain and do not work properly for 
objective functions as Eq.~\ref{eq:nodeproblem} since
the node coloring is ambiguous and has no semantic meaning, \cf Fig.~\ref{fig:fusion_abiguty}.
In the following, we propose a more suitable fusion move for correlation
clustering which works on the edge domain.
%
Given two proposal solutions $y'$ and $y''$,
$\mathcal{C}$ is the set of edges
which are uncut in $y'$ and $y''$.
%
\begin{align}
\breve{y}_{ij}    & = \max\{ y_{ij}', y_{ij}''\}  & \forall {ij}\in E\\  % y' \cup y'' \\
\mathcal{E}_0  & =  \{ (i, j) \; | \; \breve{y}_{ij} = 0 \}
\end{align}
%
The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
with additional \emph{must-link constraints} for all edges in $\mathcal{E}_0$.
%
\begin{align}
  y^* &= \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
      &\quad \textrm{s.t.} \quad y_{ij} = 0 & \forall (i, j) \in \mathcal{E}_0 \nonumber
\end{align}
%
By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy,
because $y'$ and $y''$ are feasible solutions for problem~\ref{eq:fusion_move_a}.
%\begin{align}
%  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
%\end{align}
%

@@

\noindent \textbf{Randomized HierarchicalClustering (RHC):}
%\subsubsection{Randomized HierarchicalClustering (RHC)}
%
To generate fast energy aware proposals we can use energy
based hierarchical clustering (EHC) as defined in sec.~\ref{sec:ehc}.
EHC follows the energy function, therefore the \emph{quality}
of the proposals is high.
To get \emph{diversity} among the different proposal,
we add normal distributed noise  $\mathcal{N}(0, \sigma_{ehc})$
to each edge weight.
To get proposals of the desired \emph{size}, we use a
different stop condition in EHC, and stop iff a certain number of connected
components is reached.

@@

\noindent \textbf{Randomized Watersheds (RWS):}
%\subsubsection{Randomized Watersheds (RWS)}
Watersheds have become quite popular for
graph segmentation and have a strong connection
to energy minimization~\cite{couprie_2011}.
%
The edge weighted watershed algorithm~\cite{meyer_2013}
with random seeds can be used to get
cheap proposals.
To improve \emph{quality} we do not use $n$ seeds distributed uniformly
over all nodes but use the following.
%
Draw $n/k$ negative edges,  and give the endpoints a different seed.
Doing so, a random subset of negative edges is forced
to be cut within each proposal.
For additional \emph{diversity}, noise $\mathcal{N} (0, sigma_{ws})$
can be added to the edge weighs.

@@

For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}
\small{{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}
}
of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{https://github.com/opengm/opengm}}.
For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we try the public available implementation in OpenGM\footref{opengm-master}
of Kappes~\etal. We realize that their implementation has some limitations on large problems and make the following modifications.
Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
This procedure is one magnitude faster, but might cause a few extra outer iterations.
In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
We use the public available code of Micha Elsner\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
While this implementation uses full adjacency matrixes it does not scale as well as the algorithm can and therefor can not be applied on all datasets.
We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.
